Analysis and elimination of bottlenecks in parallel algorithm for solving global optimization problems

### 2022-04-15 2022/RSD/paper.tex
Обновлено описание Метода Хука-Дживса

if $\varphi(\bar{y} + he^i) < \varphi(\bar{y})$ then set $\bar{y} = \bar{y} + he^i$ else if $\varphi(\bar{y} - he^i) < \varphi(y)$ then $\bar{y} = y - he^i.$

@@

Step 0. Set the starting point $t^0$, the parameter of the method $\varepsilon > 0$, the parameter of constructing the configuration $h\gg\varepsilon$, and the parameter $\alpha=2$ of the increasing of the step, e.g. $\alpha=2$.

@@

Step 3. If $\varphi(t^{k+1}) < \varphi(t^{k})$ then $k:=k+1$ and go to Step 4, else if $h \leq \varepsilon$, stop the search, if $h > \varepsilon$ then further actions depend on the  way how the point $y^{k+1}$ was constructed: whether the configuration was constructed using the step by sample (in this case, $k > 0$) or it was constructed from the point $t^0$(in this case, $k=0$). If $k=0$, cut $h$ in half ($h=h/2$) and go to Step 1. If $k>0$, set $t^0 = t^k, k=0$ and also go to Step 1.

Step 4. Perform the step by direction $y^{k+1} = t^k + \alpha (t^k - t^{k-1})$ and go to Step 2.

>>>>

\>\>\>\> if $\varphi(\bar{y} + he^i) < \varphi(\bar{y})$ then

\>\>\>\>\>\>\>\> set $\bar{y} = \bar{y} + he^i$

\>\>\>\> else if $\varphi(\bar{y} - he^i) < \varphi(y)$ then

\>\>\>\>\>\>\>\> set $\bar{y} = y - he^i.$

@@

Step 0. Set the starting point $t^0$, the parameter of the method $\varepsilon > 0$, the parameter of constructing the configuration $h\gg\varepsilon$, and the parameter $\alpha = 2$ of the increasing of the step, e.g. $\alpha = 2$.

@@

Step 3. Determine the next step

\>\>\>\> if $\varphi(t^{k + 1}) < \varphi(t^{k})$ then

\>\>\>\>\>\>\>\> $k = k + 1$ and go to Step 4,

\>\>\>\> else

\>\>\>\>\>\>\>\> if $h \leq \varepsilon$ then

\>\>\>\>\>\>\>\>\>\>\>\>  stop the search

\>\>\>\>\>\>\>\> else if $h > \varepsilon$ then

\>\>\>\>\>\>\>\>\>\>\>\> if $k = 0$ then

\>\>\>\>\>\>\>\>\>\>\>\>\>\>\>\> $h = h / 2$ and go to Step 1.

\>\>\>\>\>\>\>\>\>\>\>\> else if $k > 0$ then

\>\>\>\>\>\>\>\>\>\>\>\>\>\>\>\> set $t^0 = t^k, k = 0$ and go to Step 1.

Step 4. Perform the step by direction $y^{k + 1} = t^k + \alpha (t^k - t^{k - 1})$ and go to Step 2.
